\documentclass[11pt]{article} 
\input{cv_style.tex} 

\begin{document}
	
	\title{Dr. Natalie B. Hogg} % Print the main header
	
	\textbf{Postdoctoral researcher in cosmology at the \href{https://www.ast.cam.ac.uk/}{Institute of Astronomy}, University of Cambridge}\\ \\
	\textbf{Email:} \href{mailto:nbh25@cam.ac.uk}{nbh25@cam.ac.uk} | \textbf{Phone:} +44 7414 216040 | \textbf{Website:} \href{nataliebhogg.com}{nataliebhogg.com} | \textbf{Github:} \href{https://github.com/nataliehogg}{\faGithub} 
	
	%\textbf{Area of research:} 12
	
	%%----------------------------------------------------------------------------------------
	%%	PERSONAL PROFILE
	%%----------------------------------------------------------------------------------------
	%
	%\section{Personal Profile}
	%
	%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis elementum nec dolor sed sagittis. Cras justo lorem, volutpat mattis lacus vel, consequat aliquam quam. Interdum et malesuada fames ac ante ipsum primis in faucibus. Integer blandit, massa at tincidunt ornare, dolor magna interdum felis, ac blandit urna neque in turpis.
	%
	
	
	%----------------------------------------------------------------------------------------
	%	EMPLOYMENT HISTORY SECTION
	%----------------------------------------------------------------------------------------
	
	\section{Employment}
	
	\job
	{Oct 2025 --}{present}
	{Institute of Astronomy, University of Cambridge}
	{https://www.ast.cam.ac.uk/}
	{Postdoctoral researcher}
	{Building likelihood-free inference techniques for strong lensing with Prof. Will Handley.}
	
	\job
	{Oct 2023 --}{Oct 2025}
	{Laboratoire univers et particules, Universit\a'{e} de Montpellier}
	{https://www.lupm.in2p3.fr/}
	{Postdoctoral researcher}
	{Modelling strong lensing images for cosmology with Prof. Julien Larena.}
	
	\job
	{Feb 2022 --}{Oct 2023}
	{Institut de physique th\a'{e}orique, Paris-Saclay}
	{https://www.ipht.fr/en/}
	{Postdoctoral researcher}
	{Developing theoretical applications of strong lensing to cosmology, with Dr. Pierre Fleury.}
	
	\job
	{Jun 2021 --}{Feb 2022}
	{Instituto de f\a'{i}sica t\a'{e}orica, Universidad Autonoma de Madrid}
	{https://www.ift.uam-csic.es/en}
	{Postdoctoral researcher}
	{Working on applications of strong lensing and gravitational waves to cosmology, with Dr. Pierre Fleury and Dr. Matteo Martinelli.}
	
	\section{Education}
	
	\tabbedblock{
		\bf{2017 --  2021} \> \textbf{PhD in Cosmology}, University of Portsmouth \\[5pt]
		\> Thesis: \href{https://researchportal.port.ac.uk/portal/files/27089196/natalie_hogg_thesis.pdf}{Beyond $\Lambda$CDM: current and future constraints on alternative cosmological models} \\
		\>\+ Supervisors: Dr. Marco Bruni, Prof. David Wands, Prof. Robert Crittenden
	}
	
	%------------------------------------------------
	
	\tabbedblock{
		\bf{2013 -- 2017} \> \textbf{MPhys Astrophysics \nth{1} class hons.}, Aberystwyth University\\
		\>\+ with \textbf{Breen Prize} for best Master's dissertation in physics\\[5pt]
		Master's dissertation: \href{https://nataliebhogg.files.wordpress.com/2017/06/dynamical_de_nbh.pdf}{Dynamical models of dark energy \& their background cosmological evolution}\\
		Supervisor: Prof. Carsten van de Bruck (University of Sheffield; supervised remotely)
	}
	
	
	\section{Leadership \& service}
	
	\tabbedblock{
		\bf{Ongoing} \> \textbf{Referee} for MNRAS, JCAP, OJA, ApJ \& PDU.}
		
	\tabbedblock{
		\bf{2025 -- present} \> \textbf{Co-lead}, \href{https://cosmos.astro.caltech.edu/page/cosmosweb}{COSMOS-Web} Lensing Working Group}
	
	\tabbedblock{
		\bf{2024} \> \textbf{Organiser}, \href{https://beyondmainlens.sciencesconf.org/}{Strong Lensing Beyond the Main Lens workshop}, Montpellier.}
		
	\tabbedblock{
			\bf{2023 -- 2024} \> \textbf{Organiser}, LUPM cosmology journal club.}
	
	\tabbedblock{
		\bf{2022 -- 2023} \> \textbf{Organiser}, IPhT cosmology \& gravity journal club and IPhT cosmology seminar series.}
	
	\tabbedblock{
		\bf{2020} \> \textbf{Chair}, local organising committee, \href{https://sites.google.com/port.ac.uk/south-coast-cosmology/home}{South Coast Cosmology meeting}, University of Portsmouth.}
	
	\tabbedblock{
		\bf{2019} \> \textbf{Member}, local organising committee, \href{https://sites.google.com/port.ac.uk/frominfinitytozero}{A History of the Universe in Redshift} conference.}
	
	\tabbedblock{
		\bf{2018 -- 2019} \> \textbf{PhD student representative}, ICG management committee \& Faculty Research Degrees committee,\\ \>\+University of Portsmouth.}
	
	%----------------------------------------------------------------------------------------
	
	
	\section{Major awards}
	\tabbedblock{
		\bf{2021} \> \textbf{G-Research quantitative research grant}: £2000\\
		\>\+ Hardship grant from major \href{https://www.gresearch.co.uk/article/our-may-grant-winners/}{financial technology company}
	}
	\tabbedblock{
		\bf{2017} \> \textbf{Breen Prize}: £2000\\
		\>\+ Best Master's dissertation in physics, Aberystwyth University
	}
	
	Plus \textbf{travel grants} awarded over the period 2017 -- 2020 from STFC, EU COST-Action CANTATA and Santander Bank totalling approximately £6000.
	
	\section{Highlighted talks}
	\tabbedblock{
		\bf{Apr 2025} \> \textbf{Strong and weak lensing for cosmology}\\
		\>\+ Invited colloquium, CEICO, Prague
	}
	
	\tabbedblock{
		\bf{Aug 2023} \> \textbf{Strong and weak lensing for cosmology}\\
		\>\+ Invited plenary talk, ``Lensing at Different Scales'' workshop, University of Chicago
	}
	\tabbedblock{
		\bf{Apr 2023} \> \textbf{The weak lensing of strong lensing: a new cosmological probe} ~\href{https://astrotube.obspm.fr/w/ca0a828e-b3d8-45a9-ba63-f8ce33f3072e}{\faYoutubePlay}\\
		\>\+ Invited seminar, LUTH, Observatoire de Paris
	}
	\tabbedblock{
		\bf{Sep 2022} \> \textbf{Dancing in the dark: detecting a population of distant primordial black holes}\\
		\>\+ Invited seminar, IAS, Orsay
	}
	\tabbedblock{
		\bf{Apr 2022} \> \textbf{The distance duality relation: violations, constraints and biases}\\
		\>\+ Invited seminar, IAP, Paris
	}
	Since 2017, I have given 21 invited talks, contributed talks at 20 conferences and workshops, won 3 best talk prizes and given 5 outreach talks, including a Youtube video on the topic of standard sirens which has over 15,000 views ~\href{https://www.youtube.com/watch?v=DX2MiU2rX38}{\faYoutubePlay}.
	%\\
	%\textit{`Thanks ever so much for a fabulous presentation yesterday! It was incredible how you were able to present complex theories in such an accessible way.'} --- Feedback after a recent outreach talk on the history of general relativity and cosmology.
	%----------------------------------------------------------------------------------------
	%	IT/COMPUTING SKILLS SECTION
	%----------------------------------------------------------------------------------------
	
	
	\section{Supervision, mentorship and teaching}
	
	\tabbedblock{
		\bf{Supervision} \> Fabio Mongillo, undergraduate student research project, 2025.  \\
	  \> Jason Makechemu, undergraduate student research project, 2022. \\
	  \> Marco Sebastianutti, PhD student at the University of Sussex, 2022 -- 2023.}
	
	\tabbedblock{
		\bf{Mentorship} \> Giacomo Queirolo, postdoc at  the Universit\a'{e} de Montpellier, since 2024.
		\\
		\>\+ Th\a'{e}o Duboscq and Daniel Johnson, PhD students at the Universit\a'{e} de Montpellier, since 2023.}
	
%	\section{Summary of publications}
%	
%	23 papers; 7 first author, 1 single author (published as a \textit{Letter}).\\
%	Total citations: 398 --- Mean citations: 33.2 --- h-index: 10.\\
%	Numbers from \href{https://inspirehep.net/literature?sort=mostrecent&size=25&page=1&q=a
%			\%20n\%20hogg&author_count=10\%20authors\%20or\%20less\&ui-citation-summary=true}{Inspire-HEP}, for published papers with fewer than ten authors.\\
	
	\tabbedblock{
		\bf{Teaching} \> Lab demonstrator for Computational Physics course; coursework and exam marking for various\\
		\>\+ physics courses during my PhD (2017 -- 2019).}
	
%	\section{Open-source software development}
%	
%	\skillgroup{\texttt{lenstronomy}~\href{https://github.com/lenstronomy}{\faGithub}}
%	{
%		\href{https://github.com/lenstronomy/lenstronomy/graphs/contributors?type=a}{\textbf{Top 4 contributor}} to this open-source Python package for strong gravitational lensing analysis.\\
%		$\rightarrow$ I led the implementation of a new  sub-package for line-of-sight effects. \\
%		$\rightarrow$ I implemented the \texttt{zeus} ensemble slice sampler for MCMC parameter inference.\\
%		$\rightarrow$ I initiated a restructuring of the MCMC sub-package to make it easier and more intuitive to use.
%	}
%	
%	\skillgroup{\texttt{tdcosmo\_ext}~\href{https://github.com/nataliehogg/tdcosmo_ext}{\faGithub}}
%	{
%		Sole developer of this external strong lensing likelihood package for the Bayesian analysis software \texttt{Cobaya}.
%	}
%	
%	%------------------------------------------------
%	
%	\skillgroup{\texttt{analosis}~\href{https://github.com/nataliehogg/analosis}{\faGithub}}
%	{
%		Lead developer of this Python wrapper for \texttt{lenstronomy}, created to systematically generate and analyse large catalogues of strong lensing images.
%	}
%	
%	%------------------------------------------------
%	
%	\skillgroup{\texttt{darksirens}~\href{https://gitlab.com/matmartinelli/darksirens}{\faGitlab}}
%	{
%		Co-developer of this open-source Python package for creating mock gravitational wave event catalogues.
%	}
%	
%	Experienced user of Python, Fortran, Bash, Git and HPC (SLURM, PBS). 
%	
%	Other codes and software used includes \texttt{astropy}, \texttt{CAMB}, \texttt{CosmoMC}, \texttt{Cobaya}, \texttt{emcee}, \texttt{zeus}, \texttt{dynesty} and \texttt{Polychord}.
	
	%----------------------------------------------------------------------------------------
	%	INTERESTS SECTION
	%----------------------------------------------------------------------------------------
	
	
	

%	\section{\LARGE{Annex}}
%	
%	\renewcommand\refname{Publications}
%	\bibliographystyle{unsrturl}
%	\nocite{*}
%	\bibliography{mypapers}
%	
%	*PhD student at the time of publication whom I mentored. \\
%	
%	\textbf{Bibliometrics}:
%	%\begin{itemize}
%	%	\item Total citations: 296
%	%	\item Mean citations: 26.9
%	%	\item h-index: 8
%	%\end{itemize}
%	Total citations: 296 --- Mean citations: 26.9 --- h-index: 8.
%	Numbers from \href{https://inspirehep.net/literature?sort=mostrecent&size=25&page=1&q=a%20n%20hogg&author_count=10%20authors%20or%20less&ui-citation-summary=true}{Inspire-HEP}, for published papers with fewer than ten authors.\\
%	
%	I also contributed to the astrostatistics section of the 2021 \href{https://arxiv.org/abs/2110.10074}{EUCAPT} White Paper, and am a signatory of the Snowmass 2021 \href{https://arxiv.org/abs/2203.06142}{Cosmology Intertwined} White Paper.
%	

	
\end{document}